HMM Model development

### 2020-05-07 dev/hmm_model_devel.Rmd
Preparing scaffold for brms predictors

```{r}
data <- hmm_simulator(10, 20, 2)

improving_data <- data$true$true_improving %>% as.data.frame() %>% mutate(day = 1:n()) %>% pivot_longer(starts_with("V"), names_to = "patient", values_to = "improving") %>% filter(improving)

data$true$true_base_states %>% as.data.frame() %>% mutate(day = 1:n()) %>% pivot_longer(starts_with("V"), names_to = "patient", values_to = "breathing") %>% mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + geom_tile(data = improving_data, width = 1, height = 0.1, fill = "gray") + ggtitle("True - gray lines for improving")

data$observed$observations %>% as.data.frame() %>% mutate(day = 1:n()) %>% pivot_longer(starts_with("V"), names_to = "patient", values_to = "breathing") %>% mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + ggtitle("Observed")
```

@@

data <- hmm_simulator(10, 20, 2)

@@

```{r}
sbc_res <- sbc(model, generator = function() {hmm_simulator(10, 20, 2) }, N_steps = 100, control = list(adapt_delta = adapt_delta))

@@

sbc_res$params %>% filter(grepl("rates", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("sensitivity", param_name)) %>% plot_sbc_params()
#sbc_res$params %>% filter(grepl("initial", param_name)) %>% plot_sbc_params()

>>>>

```{r}
data <- hmm_simulator(10, 20, 4, use_noisy_states = TRUE)

improving_data <- data.frame(day = data$observed$times, patient = data$observed$patients, improving = data$true$true_improving) %>% filter(improving)

data.frame(day = data$observed$times, patient = data$observed$patients, breathing = data$true$true_base_states) %>%
  mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + geom_tile(data = improving_data, width = 1, height = 0.1, fill = "gray") + ggtitle("True - gray lines for improving")

data.frame(day = data$observed$times, patient = data$observed$patients, breathing = data$observed$obs_states) %>%
  mutate(breathing = factor(breathing, 1:data$observed$N_states_observed, ordered = TRUE)) %>%
  ggplot(aes(x = day, y = patient, fill = breathing)) + geom_tile(width = 1, height = 0.5) + ggtitle("Observed")
```

@@

data <- hmm_simulator(10, 20, 2, use_noisy_states = TRUE)

@@

```{r}
sbc_res <- sbc(model, generator = function() {hmm_simulator(10, 20, 2, use_noisy_states = FALSE) }, N_steps = 100, control = list(adapt_delta = adapt_delta))

@@

sbc_res$params %>% filter(grepl("rates", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("sensitivity", param_name)) %>% plot_sbc_params()
sbc_res$params %>% filter(grepl("other_observations_probs", param_name)) %>% plot_sbc_params()
